%-------------------------
% Resume in LaTeX
% Author : Ketan Dhoka
% Based on: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Repository section command
\newcommand{\resumeRepoHeading}[2]{
    \vspace{2pt}
    \item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \colorbox{black!10}{\parbox{0.97\textwidth}{\textbf{#1} \hfill \textit{\small #2}}}
    \end{tabular*}\vspace{-3pt}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ketan Dhoka} \\ \vspace{1pt}
    \small \textbf{Lead iOS Developer $|$ Technical Lead} \\ \vspace{3pt}
    \small Pune, India $|$ +91-8956367006 $|$ \href{mailto:ketandhoka16@gmail.com}{\underline{ketandhoka16@gmail.com}} $|$
    \href{https://linkedin.com/in/ketandhoka}{\underline{linkedin.com/in/ketandhoka}}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item[] \small{Technical Lead with 12+ years of experience building high-performance iOS applications using Swift, SwiftUI, and UIKit. Expertise in modernizing legacy systems with Swift Concurrency (async/await, TaskGroup) and designing scalable architectures using MVVM and Clean Architecture. Proven track record of delivering enterprise-grade solutions for global clients, significantly improving application performance, stability, and maintainability. Strong experience in Agile environments and advanced debugging, with a focus on leveraging AI-assisted development to improve productivity and code quality.}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Technical Lead}{Nov 2022 -- Present}
      {Wipro Technologies Pvt. Ltd.}{Bengaluru, India}
      \vspace{2pt}
      \small{\textit{Client: Apple Inc. (Customer Systems)}}
      \resumeItemListStart
        \resumeItem{Core contributor in developing the Media Client Framework (MCF), a reusable Cocoa framework supporting Genesys Contact Center channels for the voice media channel}
        \resumeItem{Designed and maintained abstract business logic layers, exposing high-level Swift APIs consumed across multiple Apple internal applications}
        \resumeItem{Enabled integration across applications used by over 125,000 advisors for Apple Reusable Contact Center}
        \resumeItem{Developed scalable voice media channel operations, including session handling and real-time workflows}
        \resumeItem{Built the ARCCVoice Swift Package for voice and video communication infrastructure}
        \resumeItem{Led architectural discussions and cross-team collaboration across engineering groups}
        \resumeItem{Managed release cycles, UAT coordination, and production support}
      \resumeItemListEnd

    \resumeSubheading
      {Senior iOS Developer}{Apr 2022 -- Jul 2022}
      {Oyo Technologies Pvt. Ltd.}{India}
      \resumeItemListStart
        \resumeItem{Developed and enhanced the TOD sports and entertainment live streaming application}
        \resumeItem{Optimized UI responsiveness and overall application performance}
      \resumeItemListEnd

    \resumeSubheading
      {Senior iOS Developer}{May 2017 -- Apr 2021}
      {JetSynthesys Pvt. Ltd.}{India}
      \resumeItemListStart
        \resumeItem{Delivered consumer and enterprise applications across multiple domains including sports, wellness, e-commerce, and media}
        \resumeItem{Key projects: 100MB, ThinkRight.me, Wakau, Channel Fight (DRM), Nordisk Matas, Leasy}
        \resumeItem{Implemented Live Streaming and MQTT protocol for a real-time one-to-one chat experience with Sachin Tendulkar}
        \resumeItem{Developed the DigiAdz advertisement SDK and Jet Analytics framework, both adopted across multiple apps}
      \resumeItemListEnd

    \resumeSubheading
      {iOS Developer}{Apr 2014 -- Feb 2017}
      {Praxify Technologies Pvt. Ltd.}{India}
      \resumeItemListStart
        \resumeItem{Developed iPad-based EMR/EHR healthcare systems for clinical workflows}
      \resumeItemListEnd

    \resumeSubheading
      {iOS Developer}{Apr 2013 -- Dec 2013}
      {Iauro Technologies Pvt. Ltd.}{India}
      \resumeItemListStart
        \resumeItem{Projects: Benchprep, Servme, Goel Ganga, Check Content}
      \resumeItemListEnd

    \resumeSubheading
      {iOS Developer}{Oct 2011 -- Nov 2012}
      {Xerces Technologies Pvt. Ltd.}{India}
      \resumeItemListStart
        \resumeItem{Projects: Fantasy Wallpaper, Rotary Club Finder, Test Factory}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming}{: Swift, Objective-C} \\
     \textbf{Platforms}{: iOS, macOS} \\
     \textbf{Frameworks}{: UIKit, AppKit, SwiftUI (state management, data flow), Cocoa, Cocoa Touch, Core Animation, Foundation} \\
     \textbf{Architecture}{: MVC, MVVM, clean and modular architecture, reusable components, SOLID principles} \\
     \textbf{Concurrency}{: Swift Concurrency (async/await, Task, TaskGroup, async let, Actors, MainActor), structured concurrency, GCD, multithreading, thread safety, memory management, performance optimization} \\
     \textbf{Networking \& APIs}{: REST APIs, URLSession, JSON parsing, Firebase, APNs} \\
     \textbf{Debugging \& Profiling}{: LLDB, breakpoints, View Debugger, Memory Graph, Instruments} \\
     \textbf{Build \& Dependencies}{: Swift Package Manager (SPM), CocoaPods} \\
     \textbf{Tools \& Collaboration}{: Xcode, Git, GitHub, SVN, Jira, Radar} \\
     \textbf{AI-Assisted Development}{: Code generation, debugging assistance, performance analysis, PR review support}
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {G.H. Raisoni College of Engineering \& Management}{India}
      {B.E. in Computer Engineering}{2011}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}